A Reproducible Workflow with RMarkdown, Git, Make & Docker

### 2019-08-12 rr-flow.Rmd
change title to reflect the broad scope

---
title: "Reproducible Research with Docker"
author: "Andreas Brandmaier & Aaron Peikert"
date: "8/6/2019"
output: html_document
---

>>>>

---
title: "A Reproducible Workflow with RMarkdown, Git, Make & Docker"
shorttitle: "Reproducible Workflow"
author: "Andreas Brandmaier & Aaron Peikert"
date: "8/6/2019"
output: html_document
---
